

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingWithoutItem}[4]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \vspace{5pt} \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*} 
}




\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

% Custom command for empty circle
\newcommand{\emptycircle}{\tikz[baseline=-0.5ex]\draw[fill=white,draw=black] circle (0.7ex);}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Muhammad Soban Anjum}} & Email : \href{mailto:muhammadsobananjum1@gmail.com}{muhammadsobananjum1@gmail.com} \vspace{7pt}
  \\   
  \href{https://www.linkedin.com/in/muhammadsobananjum}{Linkedin: https://www.linkedin.com/in/muhammadsobananjum} & 
  Mobile : \href{tel:+971-544750584}{+971-544750584}  \vspace{7pt}
  \\ 
  \href{https://github.com/sobananjum}{Github: https://github.com/sobananjum} & {\faMapMarker}  Sharjah, United Arab Emirates \\
\end{tabular*}



%
%--------PROGRAMMING SKILLS------------
\section{Summary}
% 	\resumeSubHeadingListStart
% 	\resumeSubItem{Languages}{Java, C++, Python, C, SQL, Unix scripting}
% 	\resumeSubItem{Tools}{Kubernetes, Docker, Springboot, GIT, JIRA, Matlab, XCode, Postgres }
% \resumeSubHeadingListEnd
\vspace{2pt}

Senior Mobile App Developer with expertise in Flutter, iOS, Android, and React Native. Proficient in Java, Dart, multithreading, and data structures. Skilled in functional programming, UI/UX design, and responsive layouts. Strong track record of creating seamless cross-platform apps using Flutter's framework. Experienced in API integration, state management, and collaborative teamwork.


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
    {EXAGIC}{Remote}
    {Senior Flutter Developer}{September 2023 - Current}
    \vspace{2pt}
   \begin{itemize}
    \item Develop and deploy NFC-enabled mobile applications for Android and iOS platforms.
    \item Integrate REST APIs to enable seamless data exchange between mobile apps and backend services.
    \item Manage the entire app lifecycle, from development to deployment on Google Play Store and Apple App Store, while ensuring continuous maintenance and updates.
   
\end{itemize}
  
    \resumeSubheading
    {DEVELOPLOGIX}{Islamabad, Pakistan}
    {Software Developer}{April 2022 -  August 2023}
    \vspace{2pt}
   \begin{itemize}
    \item Developed and maintained software solutions using PostgreSQL, MongoDB, Redis, NodeJs, Laravel, and more.
    \item Led efforts in continuous integration and continuous delivery (CI/CD), streamlining development processes.
    \item Leveraged Amazon Web Services (AWS) and Google Cloud Platform (GCP) to deliver scalable solutions.
    \item Explored blockchain and augmented reality (AR) technologies to drive innovation and user engagement.
\end{itemize}
      
    \resumeSubheading
		{PARITYZONE}{Rawalpindi, Pakistan}
		{Junior Android Developer}{Nov 2021 -  March 2022}
	 \vspace{2pt}
    \begin{itemize}
    \item Developed Android applications using Kotlin, XML, and Java, ensuring seamless user experiences.
    \item Contributed significantly to the development and maintenance of mobile applications. 
    \end{itemize}




%--------PROGRAMMING SKILLS------------
\section{Key Skills}


\emptycircle\ Flutter \quad \emptycircle\ Dart \quad \emptycircle\ Mobile Application Development \quad \emptycircle\ Kotlin \quad
\emptycircle\ Android \quad \emptycircle\ Java \quad \emptycircle\ React Native \quad \emptycircle\ iOS \\ \vspace{4pt} 
\quad \emptycircle\ API Development \quad
\emptycircle\ Bloc \quad \emptycircle\ Riverpod \quad \emptycircle\ Provider \quad \emptycircle\ GetX \quad \emptycircle\ GitHub \quad
\emptycircle\ GraphQL \quad \emptycircle\ Clean Coding \\ \vspace{4pt}
\emptycircle\ Functional Programming 
 \quad \emptycircle\ PostgresSQL \quad \emptycircle\ MongoDB \quad \emptycircle\ Redis \quad
\emptycircle\ NodeJs \quad \emptycircle\ Laravel \quad \emptycircle\ Svelte \quad \emptycircle\ Supabase \\ \vspace{4pt} 
\quad \emptycircle\ Blockchain \quad
\emptycircle\ Google Maps API \quad \emptycircle\ NextJs \quad \emptycircle\ CI/CD \quad 
\emptycircle\ Bluetooth Low Energy \quad \emptycircle\ NFC \quad \emptycircle\ Leadership \\ \vspace{4pt}
\emptycircle\ UI/UX Design \quad \emptycircle\ Git \quad \emptycircle\ Amazon Web Services (AWS) \quad \emptycircle\ Google Cloud Platform (GCP)  \quad \emptycircle\ Software Design \\ \vspace{4pt}
\quad \emptycircle\ Augmented Reality (AR) \quad \emptycircle\ Contabo \quad \emptycircle\ MySQL \quad \emptycircle\ PHP \quad
\emptycircle\ XML

% \emptycircle\ Bloc \quad \emptycircle\ Riverpod \quad \emptycircle\ Provider \quad \emptycircle\ GetX \quad \emptycircle\ GitHub \quad
% \emptycircle\ GraphQL \quad \emptycircle\ Clean Coding \quad \emptycircle\ Functional Programming \\ \vspace{2pt} \quad \emptycircle\ PostgreSQL \quad 
% \emptycircle\ MongoDB \quad \emptycircle\ Reactive Programming \quad \emptycircle\ iOS \quad \emptycircle\ Near-field Communication (NFC) \\ \vspace{2pt}
% \emptycircle\ Software Design \quad \emptycircle\ Contabo \quad \emptycircle\ MySQL \quad \emptycircle\ PHP \quad \emptycircle\ Laravel \quad
% \emptycircle\ CI/CD \quad \emptycircle\ Supabase \quad \emptycircle\ Svelte \quad
% \emptycircle\ Redis \\ \vspace{2pt} \quad \emptycircle\ NodeJs \quad \emptycircle\ Bluetooth Low Energy \quad \emptycircle\ Amazon Web Services (AWS) \quad
% \emptycircle\ Google Cloud Platform (GCP) \quad \\ \vspace{2pt} \emptycircle\ NextJs   \emptycircle\ Blockchain \quad \emptycircle\ Google Maps API 
% \emptycircle\ Git \quad \emptycircle\ React Native \quad \emptycircle\ Augmented Reality (AR) \quad \\ \vspace{2pt} \quad \emptycircle\ API Development \vspace{2pt} \quad
% \emptycircle\ Leadership \quad \emptycircle\ Flutter \quad \emptycircle\ Dart \quad \emptycircle\ Mobile Application Development  \quad
% \emptycircle\ Kotlin \quad \emptycircle\ XML \quad \emptycircle\ Android \quad \emptycircle\ Java

	% \resumeSubHeadingListStart
	% \resumeSubItem{Languages}{~~~~~~PHP  C++, JavaScript, SQL, JAVA, Kotlin, Dart }
 %    \vspace{3pt}
	% \resumeSubItem{Frameworks}{~~~~Flutter, React Native, JQuery, Express.js, Node.js}
 %       \vspace{3pt}
	% \resumeSubItem{Tools}{~~~~~~~~~~~~~~GitHub, Android Studio, VS Code, Atom}
 %       \vspace{3pt}
	% \resumeSubItem{Platforms}{~~~~~~~Linux, Windows, MacOS}
 %       \vspace{3pt}
	% \resumeSubItem{Soft Skills}{~~~~~~~Adaptability, Team Work, Quick Learner, Problem Solver, Analytical Skills, Project Management}

\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{tellz.me}{

tellz.me® utilizes QR codes, NFC, and Bluetooth beacons for targeted advertising. Employs interest-based content filtering and push notifications. Enhances marketing strategies and user engagement.


 \href{https://play.google.com/store/apps/details?id=com.app.tmpage&pli=1}{\faAndroid}
 \href{https://play.google.com/store/apps/details?id=com.app.tmpage&pli=1}{ https://play.google.com/store/apps/details?id=com.app.tmpage}
 \vspace{2pt}
 \\ 
 \href{https://apps.apple.com/de/app/tellz-me-page/id1622993070}{\faApple}
  \href{https://apps.apple.com/de/app/tellz-me-page/id1622993070}{ https://apps.apple.com/de/app/tellz-me-page/id1622993070}
  \vspace{2pt}
 \\
  \href{https://www.tellz.me/}{\faCode}
  \href{https://www.tellz.me/}{https://www.tellz.me/}
}
\vspace{5pt}
\resumeSubItem{GoDropMe}{ 

Streamlines package posting, ridesharing, and scheduling. Facilitates real-time tracking, secure Stripe payments, and efficient communication for drivers and passengers. Simplifies logistics and enhances user experience.

 \href{https://play.google.com/store/apps/details?id=com.app.tmpage&pli=1}{\faAndroid}
 \href{https://play.google.com/store/apps/details?id=com.codetivelab.godropme&pli=1}{https://play.google.com/store/apps/details?id=com.codetivelab.godropme}
  \vspace{2pt}
 \\ 
  \href{https://go-drop-me.web.app}{\faCode}
  \href{https://go-drop-me.web.app}{https://go-drop-me.web.app}
}
\vspace{5pt}
\resumeSubItem{Check-In}{

Check-In enables users to discover nearby basketball courts and check in to share real-time court availability with fellow players. Enhances coordination for seamless pick-up games.

\href{https://play.google.com/store/apps/details?id=com.developlogix.checkinapp}{\faAndroid}
\href{https://play.google.com/store/apps/details?id=com.developlogix.checkinapp}{https://play.google.com/store/apps/details?id=com.developlogix.checkinapp}
\\
}
\vspace{5pt}
\resumeSubItem {Speak and Translate}{

Speak and Translate facilitates real-time text and speech translation across multiple languages. Converts spoken and written content. Also features image-to-text conversion for seamless multilingual communication.

\href{https://play.google.com/store/apps/details?id=com.parityzone.speakandtranslate}{\faAndroid}
\href{https://play.google.com/store/apps/details?id=com.parityzone.speakandtranslate}{https://play.google.com/store/apps/details?id=com.parityzone.speakandtranslate}

}
\vspace{5pt}

\resumeSubItem {Document Scanner}{

Document Scanner effortlessly digitize and store documents, receipts, and notes using your mobile device's camera. Scan, save, and share documents on the go.

\href{https://play.google.com/store/apps/details?id=come.parityzone.documentscanner}{\faAndroid}
\href{https://play.google.com/store/apps/details?id=come.parityzone.documentscanner}{https://play.google.com/store/apps/details?id=come.parityzone.documentscanner}

}
\vspace{5pt}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  

\resumeSubheadingWithoutItem
{University Institute of Information Technology, Arid Agriculture University}{Rawalpindi, Pakistan}
{Bachelor of Science in Computer Science | CGPA: 3.39}{Aug 2017 - Oct 2021}

    
% {University Institute of Information Technology, Arid Agriculture University}{Rawalpindi, Pakistan}
%       {Bachelor of Science in Computer Science | CGPA: 3.39}{Aug 2017 - Oct 2021}
      
      
      
	   % {\scriptsize \textit{Courses: Operating Systems, Data Structures and Algorithms, Artificial Intelligence, Probability and Statistics and Computer Communication and Networks.}}
	

%-----------Awards-----------------
\section{Certifications}
\begin{description}[font=$\bullet$]
\item {Flutter Development with Riverpod} \\  \vspace{2pt} \href{https://www.udemy.com/certificate/UC-d567a635-098b-4b3f-af43-bd3654914ba4/}{https://www.udemy.com/certificate/UC-d567a635-098b-4b3f-af43-bd3654914ba4/}
\item {JavaScript Algorithms and Data Structures} \\ \vspace{2pt}  \href{https://www.freecodecamp.org/certification/fccc370662e-bccd-437a-a618-2f8664f0cac9/javascript-algorithms-and-data-structures}{https://www.freecodecamp.org/certification/fccc370662e-bccd-437a-a618-2f8664f0cac9/javascript-algorithms-and-data-structures}
\end{description}
%-------------------------------------------
\end{document}